The journey of Multiple Sequence Alignment

### 2021-08-06 MSA_Notum_journey.Rmd
add the sequences and the results for sponges

>>>>

### Hs|RYK vs Halichondria panicea TRINITY_DN396839_c0_g1_i1, transcribed RNA sequence
```{bash}
>Hp|TRINITY_DN396839_c0_g1_i1
ESCLMKGFCHQNVNPILGACMENEKQPLLVYAYSTEGNLKKFLQRCKMSEMASSYALSTQQLVYIAIQIIRGVQYLHRKR
VVHRDVATRNCVIDHQLNVKVTDTALSRDLFPNDYHCLGDNENRPVKWLAIEALLDRHFTPASDVWSFGVTMWELMTLGQ
QPYADVDPFEMATYLKEGYRIAQPINCPDELFSVMACCWSMLGEERPKLTQLQACLQDFYTALGRFI
```

### Hs|RYK vs Cymbastela stipitata TRINITY_DN14054_c0_g1_i1, transcribed RNA sequence
```{bash}
>Cs|TRINITY_DN14054_c0_g1_i1
NIASVGAVATTDFSISFPCTNTLQGRADVRVTLNFTFDFTGGTLRSLVGQVFTMTGTRVCNCTNSRCDNTEPPNDGGVNN
EIFYIVIGCVGGVILLVIMVTVLYHCIMLGMWVKRRSQDEEPLPNIEDVIPMPPYPMVTITPLSSQVPIAPLPNSPRNSF
SVPSDLSKSLRSLQSFKDLIVDRKRISIGQVLKEGVFGVMYDGYLSNAEDDVEGAIPVIIKTVKDNTPDIVVKSLLEGGG
ATRAVSHRHVLPLLAAHVSDTEQPMLLFPKTSLGTLKGLLMRCREPKRGVSLTLTTQNLVFIAGQISRGMYHLTRKGLIH
RDLAARNIYVHENLHVKIGDRGLSWDLFPSEYSRLPDGEMCPIRWMSAEVLSERKYSHYSDVWSFGVVLWELMTLGRIPY
EEVPAEDMLAMLTAGHRLSQPKNCPDELFVLMGWCWALTPTDRPRFSHLTLRLKEFHEKINAFV
```

### Hs|RYK vs Neopetrosia compacta breed sponge isolate demosponge TRINITY_DN1516_c3_g1_i2, transcribed RNA sequence
```{bash}
>Nc|TRINITY_DN1516_c3_g1_i2
RDVFVDRKRIQFGCKITEGVFGVMYDGYLTNAEDDVEGAVPVIIKTVKDNTPDVVVKSLLEGGSATRGVSHRHLLPLLAA
HASDLEQPMLLFPKTAHGSLKSLLLCSRGAQRVIPGSPFLTTQDLVFMAEQVARGMYHLTRKGLVHKDLAARNIYVHENL
HVKIGDRGLCWDFFPSEYSTLEGDQELIASPIRWMAAEVIAEKKYSHYSDVWAFGVVLWEIMTKGKIPYEDVLPEQMYSY
LTYGSRLQQPKNCPDDLFSLMGWCWALTPGDRPRFSHLTIRLKEFHERLGAFI
```

### Hs|RYK vs Dysidea avara TR158463_c0_g1_i1 transcribed RNA sequence
```{bash}
>Da|TR158463_c0_g1_i1
MKDILVDKNRIQLGELIKEGTYGRMYEGYLANTEDDVEGSVSIIVKTVSDITPDQVVASLVDGCLVLRHIQHRHILQALG
VYSNEQEPVMVLLARTTFGTLKQFLDDIRLQGGPQSSYGKLLLTQDMVFISAQIARGMYHLSRKGGIIHKDLAARNIYIH
ENLHVKIGDRGLSWDFYPDDYQVTPNGEYVPVKWASVEVLEEQQYSMYSDVWAFGVVLWEIMTVGLVPYDSVTPNELVDY
LKSGQRLTRPTNCPDDMFSIMGQCWALTPTDRPKFSHLTVGLDHFHLRLNSYI
```

hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_profile_HS_RYKvssponges_domtbl.out my_data/pfam/Pfam-A.hmm my_data/Hs_RYKvs_sponges.fasta > /dev/null
```

WIF_hmmscan <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_profile_HS_RYKvssponges_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=29;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)

About Of|1176102141 we got only one result:
### Of|1176102141 vs Cymbastela stipitata TRINITY_DN17682_c0_g1_i1, transcribed RNA sequence
```{bash}
>Cs|TRINITY_DN17682_c0_g1_i1
LPPLPSSVDEISISWHASEEVIYELHVGQDPQGVFEDPRLNIPENGTIPRNKTAFSISFPC
```

```{bash}
touch my_data/Of1176102141_vs_sponges.fasta

hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_profile_Of1176102141vssponges_domtbl.out my_data/pfam/Pfam-A.hmm my_data/Of1176102141_vs_sponges.fasta > /dev/null
```

WIF_hmmscan <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_profile_Of1176102141vssponges_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=29;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)

### Ci|198430807 vs Halichondria panicea TRINITY_DN396839_c0_g1_i1, transcribed RNA sequence
```{bash}
>Hp|TRINITY_DN396839_c0_g1_i1
ESCLMKGFCHQNVNPILGACMENEKQPLLVYAYSTEGNLKKFLQRCKMSEMASSYALSTQQLVYIAIQIIRGVQYLHRKR
VVHRDVATRNCVIDHQLNVKVTDTALSRDLFPNDYHCLGDNENRPVKWLAIEALLDRHFTPASDVWSFGVTMWELMTLGQ
QPYADVDPFEMATYLKEGYRIAQPINCPDELFSVMACCWSMLGEERPKLTQLQACLQDFYTALGRFI
```

### Ci|198430807 vs Cymbastela stipitata TRINITY_DN14054_c0_g1_i1, transcribed RNA sequence
```{bash}
>Cs|TRINITY_DN14054_c0_g1_i1
LCLRAVWVLLALYRCVCALDWFIPAAEVQRIEGEENAPALYLVRQSVVQRSTLPLSETAMNTRVMFSWAGSGLAYQFKSV
SSNPAVLMGAEFENIASVGAVATTDFSISFPCTNTLQGRADVRVTLNFTFDFTGGTLRSLVGQVFTMTGTRVCNCTNSRC
DNTEPPNDGGVNNEIFYIVIGCVGGVILLVIMVTVLYHCIMLGMWVKRRSQDEEPLPNIEDVIPMPPYPMVTITPLSSQV
PIAPLPNSPRNSFSVPSDLSKSLRSLQSFKDLIVDRKRISIGQVLKEGVFGVMYDGYLSNAEDDVEGAIPVIIKTVKDNT
PDIVVKSLLEGGGATRAVSHRHVLPLLAAHVSDTEQPMLLFPKTSLGTLKGLLMRCREPKRGVSLTLTTQNLVFIAGQIS
RGMYHLTRKGLIHRDLAARNIYVHENLHVKIGDRGLSWDLFPSEYSRLPDGEMCPIRWMSAEVLSERKYSHYSDVWSFGV
VLWELMTLGRIPYEEVPAEDMLAMLTAGHRLSQPKNCPDELFVLMGWCWALTPTDRPRFSHLTLRLKEFHEKINAFV
```

### Ci|198430807 vs Halichondria panicea TRINITY_DN874_c0_g1_i3, transcribed RNA sequence
```{bash}
>Hp|TRINITY_DN874_c0_g1_i3
LTTDMPVSDLKSSPRHSHSSISVPPALNNSLRNLHSFRDLFVHRKRISIGVVLTEGVFGVIYDGYLSNAEDDVEGVTPVI
IKTVKDNTPEIVVRSLLEGGAALRHVPHRHLLPLLACHASDSEQPMLLFPKTALGTLKTVLLRTRDNKTTPGGSQKGALA
LSTQNLVMVAAQISRGMYHLTKKGLTHRDLAARNIYIHQNLHVRIGDRGLSWDLYPEEYSQMPDGEMCPVKWMAAEVLTD
RNYSHYSDVWSFGVVLWEIMTLGKIPYSENTAEEMVALLTAGQRLSQPKNCPDDLFVLMGWCWALTPTDRPRFSHLTLRL
KEFHEKICSFV
```

### Ci|198430807 vs Dysidea avara TR158463_c0_g1_i1 transcribed RNA sequence
```{bash}
>Da|TR158463_c0_g1_i1
SLKPAVDGSLAVLTAELNKSVHSLFSMKDILVDKNRIQLGELIKEGTYGRMYEGYLANTEDDVEGSVSIIVKTVSDITP
DQVVASLVDGCLVLRHIQHRHILQALGVYSNEQEPVMVLLARTTFGTLKQFLDDIRLQGGPQSSYGKLLLTQDMVFISAQ
IARGMYHLSRKGGIIHKDLAARNIYIHENLHVKIGDRGLSWDFYPDDYQVTPNGEYVPVKWASVEVLEEQQYSMYSDVWA
FGVVLWEIMTVGLVPYDSVTPNELVDYLKSGQRLTRPTNCPDDMFSIMGQCWALTPTDRPKFSHLTVGLDHFHLRLNSYI
```

```{bash}
touch my_data/Ci_198430807_vs_sponges.fasta

hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_profile_Ci_198430807vssponges_domtbl.out my_data/pfam/Pfam-A.hmm my_data/Ci_198430807_vs_sponges.fasta > /dev/null
```

WIF_hmmscan <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_profile_Ci_198430807vssponges_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=29;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
